### 2016-01-12 p01-ch01-2012/paper.tex
Remove all `vspace`
Fix long captions in figures and tables

\begin{figure}[t]
%\begin{center}
\includegraphics[scale=0.36]{figs/seq-diag-1}
~\\[-3.5cm]ADD:\\[2.5cm]
  \caption{Adding the new MethodInvocations are performed on the Client side.}
  \label{fig:add}
%\end{center}
\end{figure}

@@

\begin{figure}[t]
~\\TAKE:\\
%\begin{center}
%\vspace{-1.3cm}
  \includegraphics[scale=0.3]{figs/seq-diag-2}
\vspace{-.7cm}
  \caption{An active object selects a method invocation based on its local scheduling policy. After a method finishes execution, the whole scenario is repeated.}
  \label{fig:take}
%\end{center}
\end{figure}

@@

\begin{figure}[t]
~\\EXECUTE:\\
% \begin{center}
% \vspace{-1.3cm}
 \includegraphics[scale=0.35]{figs/seq-diag-3}
\vspace{-.7cm}
\caption{A method invocation is executed in an interruptible process. The execution manager thread is blocked while the interruptible process is running.}
  \label{fig:execute}
% \end{center}
\end{figure}

>>>>

\begin{figure}[t]
%\begin{center}
\includegraphics[scale=0.36]{figs/seq-diag-1}
~\\[-3.5cm]ADD:\\[2.5cm]
\caption[New MethodInvocation]{Adding the new MethodInvocations are performed on the Client side.}
\label{fig:add}
%\end{center}
\end{figure}

@@

\begin{figure}[t]
~\\TAKE:\\
\begin{center}
%\vspace{-1.3cm}
  \includegraphics[scale=0.3]{figs/seq-diag-2}
% \vspace{-.7cm}
\caption[Policy-based selection of a MethodInvocation]{An active object selects a method invocation based on its local scheduling policy. After a method finishes execution, the whole scenario is repeated.}
\end{center}
\label{fig:take}
\end{figure}

@@

\begin{figure}[t]
~\\EXECUTE:\\
\begin{center}
% \vspace{-1.3cm}
 \includegraphics[scale=0.35]{figs/seq-diag-3}
% \vspace{-.7cm}
\caption[Execution of a MethodInvocation]{A method invocation is executed in an interruptible process. The execution manager thread is blocked while the interruptible process is running.}
\end{center}
\label{fig:execute}
\end{figure}

### 2016-01-12 p02-ch01-2014/paper.tex
Add publication information to chapter abstracts
Remove all `vspace`
Fix long captions in figures and tables

@@

\begin{wrapfigure}{r}{0.48\textwidth}
\vspace{-20pt}
\begin{lstlisting}[caption=main in Akka,label=lst:main:akka]
ActorSystem s = ActorSystem.create();
ActorRef pong = s.actorOf(Props.create(Pong.class));
ActorRef ping = s.actorOf(Props.create(Ping.class, pong));
ping.tell(""); // To get a Future
\end{lstlisting}
\vspace{-20pt}
\end{wrapfigure}

@@

We first describe informally the actor programming model assumed in this paper. This model is based on the
Abstract Behavioral Specification language (ABS)  
introduced in \cite{johnsen2012abs}.
ABS uses asynchronous method calls, futures, interfaces for encapsulation, 
and cooperative scheduling of method invocations inside concurrent (active) objects. 
This feature combination results in a concurrent object-oriented model which is inherently compositional.
More specifically, actors in ABS  have an identity and behave as active
objects with encapsulated data and methods which represent their state
and behavior, respectively.  Actors are the units of concurrency: conceptually an actor has a dedicated processor. Actors can only send
asynchronous messages and have queues for receiving messages.  An
actor progresses by taking a message out of its queue and processing
it by executing its corresponding method.  A method is a piece of
sequential code that may send messages.
% 
\lstset{language=Java}
\begin{wrapfigure}{r}{0.48\textwidth}
\vspace{-20pt}
\begin{lstlisting}[caption=main in ABS,label=lst:main:ABS]
ABSIPong pong;
pong = new ABSPong;
ping = new ABSPing(pong);
ping ! ping("");
\end{lstlisting}
\vspace{-20pt}
\end{wrapfigure}
% 
Asynchronous method calls use futures as dynamically generated references  to return values.
The execution of a method can be (temporarily) suspended by release statements which give rise to a form
of  cooperative scheduling of method invocations inside concurrent (active) objects.
Release statements can be conditional (e.g., checking a future for the return value).
Listings \ref{lst:ping:abs}, \ref{lst:pong:abs} and \ref{lst:main:ABS} present an implementation of ping-pong example in ABS.
By means of the statement on line 6 of Listing \ref{lst:ping:abs}
a ``ping'' object  directly calls asynchronously the \jtt{pong} method  of its ``pong'' object, and vice versa.
Such a call is stored in the message queue and the called method is executed when the message is dequeued.
Note that variables in ABS are declared by interfaces.
In ABS, \jtt{Unit} is similar to \jtt{void} in Java.

@@

\begin{figure}[t]
\begin{center}
\includegraphics[scale=.45]{figs/benchmarks}  
\end{center}
\caption{
Benchmark results of comparing sampling time of message round trips in ABS API and Akka.
An example reading of above results is that the time shows for $p(90.0000)$ reads as ``message round trips were completed under $10{\mu}s$ for $90\%$ of the sent messages''.
The first two columns show the ``minimum'' and ``mean'' message round trip times in both implementations.
}
\label{fig:benchmarks}
\end{figure}

>>>>

%

\subparagraph*{Conference Publication}
\emph{Lecture Notes in Computer Science, Volume 8803, 6th International Symposium on Leveraging Applications of Formal Methods, Verification and Validation with Specialized Techniques and Applications -- ISoLA 2014, Pages 37--53, DOI 
\smalltt{10.1007/978-3-662-45231-8\_4}}

%

@@

\begin{figure}[h]
% \begin{wrapfigure}{r}{0.48\textwidth}
% \vspace{-20pt}
\begin{lstlisting}[caption=main in Akka,label=lst:main:akka]
ActorSystem s = ActorSystem.create();
ActorRef pong = s.actorOf(Props.create(Pong.class));
ActorRef ping = s.actorOf(Props.create(Ping.class, pong));
ping.tell(""); // To get a Future
\end{lstlisting}
% \vspace{-20pt}
% \end{wrapfigure}
\end{figure}

@@

We first describe informally the actor programming model assumed in this paper. This model is based on the
Abstract Behavioral Specification language (ABS)  
introduced in \cite{johnsen2012abs}.
ABS uses asynchronous method calls, futures, interfaces for encapsulation, 
and cooperative scheduling of method invocations inside concurrent (active) objects. 
This feature combination results in a concurrent object-oriented model which is inherently compositional.
More specifically, actors in ABS  have an identity and behave as active
objects with encapsulated data and methods which represent their state
and behavior, respectively.  Actors are the units of concurrency: conceptually an actor has a dedicated processor. Actors can only send
asynchronous messages and have queues for receiving messages.  An
actor progresses by taking a message out of its queue and processing
it by executing its corresponding method.  A method is a piece of
sequential code that may send messages.
%

\lstset{language=Java}
\begin{figure}[h]
% \begin{wrapfigure}{r}{0.48\textwidth}
% \vspace{-20pt}
\begin{lstlisting}[caption=main in ABS,label=lst:main:ABS]
ABSIPong pong;
pong = new ABSPong;
ping = new ABSPing(pong);
ping ! ping("");
\end{lstlisting}
% \vspace{-20pt}
% \end{wrapfigure}
\end{figure}

Asynchronous method calls use futures as dynamically generated references  to return values.
The execution of a method can be (temporarily) suspended by release statements which give rise to a form
of  cooperative scheduling of method invocations inside concurrent (active) objects.
Release statements can be conditional (e.g., checking a future for the return value).
Listings \ref{lst:ping:abs}, \ref{lst:pong:abs} and \ref{lst:main:ABS} present an implementation of ping-pong example in ABS.
By means of the statement on line 6 of Listing \ref{lst:ping:abs}
a ``ping'' object  directly calls asynchronously the \jtt{pong} method  of its ``pong'' object, and vice versa.
Such a call is stored in the message queue and the called method is executed when the message is dequeued.
Note that variables in ABS are declared by interfaces.
In ABS, \jtt{Unit} is similar to \jtt{void} in Java.

@@

\begin{figure}[t]
\begin{center}
\includegraphics[scale=.45]{figs/benchmarks}  
\end{center}
\caption[Benchmarking comparison of ABS API and Akka]{
Benchmark results of comparing sampling time of message round trips in ABS API and Akka.
An example reading of above results is that the time shows for $p(90.0000)$ reads as ``message round trips were completed under $10{\mu}s$ for $90\%$ of the sent messages''.
The first two columns show the ``minimum'' and ``mean'' message round trip times in both implementations.
}
\label{fig:benchmarks}
\end{figure}

### 2016-01-12 p03-ch01-2015-monitoring/sec05-monitoring-model.tex
Remove all `vspace`
Fix long captions in figures and tables

We use task automata to design $M_{\alpha_s}$.
Periodically, $M_{\alpha_s}$ checks whether the service availability
is within the thresholds, taking tolerance into account
(Definition~\ref{def:service:availability}).
If the condition fails, $M_{\alpha_s}$ generates a task for monitoring platform $P$ to allocate a new resource to service $s$ with a deadline of $\tau$.
We define the period to be $\tau$.
We use the semantics of a task automata in \cite{jaghoori2010time} p. 92 in the transitions of the task automata.
Figure~\ref{fig:fsm:task:alpha} and \ref{fig:fsm:task:beta} present $M_{\alpha_s}$ and $M_{\beta_s}$.
Both $M_{\alpha_s}$ and $M_{\beta_s}$ share state with the monitoring platform $P$.
The state keeps the current number of resources for a service $s$ that is denoted by $\sigma(s)$.
All timed automata and task automata in the monitoring platform have shared access to $\sigma(s)$.
In the automata, we use a conditional statement to check the service characteristics $\alpha(s,\tau,t_c)$ or $\beta(s,\tau)$.
If the condition fails, $M_{\alpha_s}$ requests $P$ to \jtt{allocate} a new resource to $s$ and $M_{\beta_s}$ requests $P$ to \jtt{deallocate} a resource.
In addition, $M_{\alpha_s}$ triggers a new task $\jtt{verify}_\alpha$ with deadline $t_G$.
Intuitively, this means the service characteristic $\alpha(s,\tau,t_c)$ is verified to be within the expected thresholds after at most $t_G$ time.
\begin{figure}[h]
\vspace{-15pt}
\captionsetup[subfigure]{font=footnotesize}
\centering
\subcaptionbox{\scriptsize{$M_{\alpha_s}$ task automata for $\alpha(s,\tau,t_c)$}\label{fig:fsm:task:alpha}}[0.45\textwidth]{
\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=7cm,thick,scale=0.6,every node/.style={scale=0.6},level distance=20mm]
\node[state,initial]
  (a)   {};
\node[state]
  (b) [right of=a]  {};
\path[]
(a)
  edge
  node {$\bfjtt{duration}(\tau,\tau)$}
  (b)
(b)
  edge [bend right,above] 
  node [align=center] 
    {$\bfjtt{if}\big((1-\varepsilon_\alpha(s,\tau,t_c)) > \alpha(s,\tau,t_c)\big) $ \\ \{ %\\
     $P \; ! \; \jtt{allocate}(s,\tau)$ ; %\\
     $P \; ! \; \jtt{verify}_\alpha(s,t_G)$ \}
    }
  (a)
;
\end{tikzpicture}
}%
\subcaptionbox{\scriptsize{$M_{\beta_s}$ task automata for $\beta(s,\tau)$}\label{fig:fsm:task:beta}}[0.45\textwidth]{
\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=7cm,thick,scale=0.6,every node/.style={scale=0.6},level distance=20mm]
\node[state,initial]
  (a)   {};
\node[state]
  (b) [right of=a]  {};
\path[]
(a)
  edge 
  node {$\bfjtt{duration}(\tau,\tau)$}
  (b)
(b)
  edge [bend right, above] 
  node [align=center] 
       {$\bfjtt{if}\big((1-\varepsilon_\beta(s,\tau)) > \beta(s,\tau)\big) $ 
       \\ \{ %\\
        $P \; ! \; \jtt{deallocate}(s,\tau)$ ; %\\
        $P \; ! \; \jtt{verify}_\beta(s,t_G)$ \}
       }
  (a)
;
\end{tikzpicture}
}
\vspace{-10pt}
% \caption{{\scriptsize Task Automata for $\alpha(s,\tau,t_c)$ and $\beta(s,\tau)$}}
\vspace{-10pt}
\end{figure}

We use a separate task automaton for each service characteristic to verify the SLA of the service after $t_G$ time.
Respectively, $M^{\alpha}_{\jtt{V}}$ and $M^{\beta}_{\jtt{V}}$ execute tasks $\jtt{verify}_\alpha$ and $\jtt{verify}_\beta$ (Figures~\ref{fig:fsm:task:verify:alpha} and \ref{fig:fsm:task:verify:beta}).
$M^{\alpha}_{\jtt{V}}$ uses \bfjtt{await} to ensure the condition of the SLA.
In addition, the task is controlled by the scheduler using a deadline that is specified as $t_G$ in the generated task $\jtt{verify}_\alpha(s,t_G)$ in $M_{\alpha_s}$. 
If $t_G$ passes before the guard statement in \bfjtt{await} statement holds, it leads to a \emph{missed deadline}.
\begin{figure}[h]
\vspace{-20pt}
\captionsetup[subfigure]{font=scriptsize}
\centering
\subcaptionbox{\scriptsize{$M^{\alpha}_{\jtt{V}}$ to execute $\jtt{verify}_\alpha$}\label{fig:fsm:task:verify:alpha}}[0.45\textwidth]{
\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=6.5cm,thick,scale=0.6,every node/.style={scale=0.6},level distance=20mm]
\node[state,initial]
  (a)   {};
\node[state,accepting]
  (b) [right of=a]  {};
\path[]
(a)
  edge
  node [align=center] 
    {$\bfjtt{await} \; \alpha(s,\tau,t_c) \geq 1-\varepsilon_\alpha(s,\tau,t_c)$}
  (b)
;
\end{tikzpicture}
}%
\subcaptionbox{\scriptsize{$M^{\beta}_{\jtt{V}}$ to execute $\jtt{verify}_\beta$}\label{fig:fsm:task:verify:beta}}[0.45\textwidth]{
\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=6cm,thick,scale=0.6,every node/.style={scale=0.6},level distance=20mm]
\node[state,initial]
  (a)   {};
\node[state,accepting]
  (b) [right of=a]  {};
\path[]
(a)
  edge
  node [align=center] 
    {$\bfjtt{await} \; \beta(s,\tau) \geq 1-\varepsilon_\beta(s,\tau)$}
  (b)
;
\end{tikzpicture}%
}
\vspace{-10pt}
% \caption{{\scriptsize Task automata to execute $\jtt{verify}_\alpha$ and $\jtt{verify}_\beta$}}
\vspace{-10pt}
\end{figure}

@@

\begin{figure}[h]
\vspace{-20pt}
\centering
\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=4cm,thick,scale=0.7,every node/.style={scale=0.7}]
\node[state,initial]    
  (a)   {};
\node[state]
  (b) [right of=a]   {};
\node[state,accepting]
  (c) [right of=b]  {};
\path[]
(a) 
    edge    
    node {$\bfjtt{duration}(t_i,\tau)$}          
    (b)
(b) 
    edge    
    node {$\sigma(s) \gets \sigma(s) + 1$} 
    (c)
;
\end{tikzpicture}
\vspace{-15pt}
\caption{{\scriptsize{$M_{\jtt{A}_s}$: Timed Automaton to execute task type \jtt{allocate} in $M_P$}}
\vspace{-20pt}
\label{fig:fsm:alloc_s}}
\end{figure}

Then, we define $M_{\jtt{A}}$ in $M_P$ as:
$M_{\jtt{A}} = \; \parallel_s M_{\jtt{A}_s}$; i.e.
the composition of all timed automata to execute a task \jtt{allocate} for some service $s$.
% 
Similarly, we design $M_{\jtt{D}_s}$ to execute task type \jtt{deallocate} in Figure~\ref{fig:fsm:dealloc_s}.
Therefore, we also have $M_{\jtt{D}}$ in $M_P$ as: $M_{\jtt{D}} = \; \parallel_s M_{\jtt{D}_s}$.
% 
\begin{figure}[h!]
\vspace{-10pt}
\centering
\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=4cm,thick,scale=0.7,every node/.style={scale=0.7}]
\node[state,initial]    
  (a)   {};
\node[state]
  (b) [right of=a]   {};
\node[state,accepting]
  (c) [right of=b]  {};
\path[]
(a) 
    edge    
    node {$\bfjtt{duration}(t_i,\tau)$}          
    (b)
(b) 
    edge    
    node {$\sigma(s) \gets \sigma(s) - 1$} 
    (c)
;
\end{tikzpicture}
\vspace{-15pt}
\caption{{\scriptsize{$M_{\jtt{D}_s}$: Timed Automaton to execute task type \jtt{deallocate} in $M_P$}}
\vspace{-20pt}
\label{fig:fsm:dealloc_s}}
\end{figure}
%

@@

\begin{figure}[h]
\vspace{-20pt}
\centering
\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=5cm,thick,scale=0.7,every node/.style={scale=0.7}]
\node[state,initial]
  (a) {};
\node[state]
  (b) [right of=a] {};
\node[state]
  (c) [right of=b] {};
\path[]
(a)
  edge
  node {$\bfjtt{duration}(0,\tau)$}
  (b)
(b)
  edge
  node {$\sigma(s)\gets\sigma(s)-c$}
  (c)
;
\end{tikzpicture}
\vspace{-13pt}
\caption{\scriptsize{An example behavior for $M_E$}}
\label{fsm:env}
\vspace{-20pt}
\end{figure}

>>>>

We use task automata to design $M_{\alpha_s}$.
Periodically, $M_{\alpha_s}$ checks whether the service availability
is within the thresholds, taking tolerance into account
(Definition~\ref{def:service:availability}).
If the condition fails, $M_{\alpha_s}$ generates a task for monitoring platform $P$ to allocate a new resource to service $s$ with a deadline of $\tau$.
We define the period to be $\tau$.
We use the semantics of a task automata in \cite{jaghoori2010time} p. 92 in the transitions of the task automata.
Figure~\ref{fig:fsm:task:alpha} and \ref{fig:fsm:task:beta} present $M_{\alpha_s}$ and $M_{\beta_s}$.
Both $M_{\alpha_s}$ and $M_{\beta_s}$ share state with the monitoring platform $P$.
The state keeps the current number of resources for a service $s$ that is denoted by $\sigma(s)$.
All timed automata and task automata in the monitoring platform have shared access to $\sigma(s)$.
In the automata, we use a conditional statement to check the service characteristics $\alpha(s,\tau,t_c)$ or $\beta(s,\tau)$.
If the condition fails, $M_{\alpha_s}$ requests $P$ to \jtt{allocate} a new resource to $s$ and $M_{\beta_s}$ requests $P$ to \jtt{deallocate} a resource.
In addition, $M_{\alpha_s}$ triggers a new task $\jtt{verify}_\alpha$ with deadline $t_G$.
Intuitively, this means the service characteristic $\alpha(s,\tau,t_c)$ is verified to be within the expected thresholds after at most $t_G$ time.
\begin{figure}[h]
% \vspace{-15pt}
\captionsetup[subfigure]{font=footnotesize}
\centering
\subcaptionbox{\scriptsize{$M_{\alpha_s}$ task automata for $\alpha(s,\tau,t_c)$}\label{fig:fsm:task:alpha}}[0.45\textwidth]{
\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=7cm,thick,scale=0.6,every node/.style={scale=0.6},level distance=20mm]
\node[state,initial]
  (a)   {};
\node[state]
  (b) [right of=a]  {};
\path[]
(a)
  edge
  node {$\bfjtt{duration}(\tau,\tau)$}
  (b)
(b)
  edge [bend right,above] 
  node [align=center] 
    {$\bfjtt{if}\big((1-\varepsilon_\alpha(s,\tau,t_c)) > \alpha(s,\tau,t_c)\big) $ \\ \{ %\\
     $P \; ! \; \jtt{allocate}(s,\tau)$ ; %\\
     $P \; ! \; \jtt{verify}_\alpha(s,t_G)$ \}
    }
  (a)
;
\end{tikzpicture}
}%
\subcaptionbox{\scriptsize{$M_{\beta_s}$ task automata for $\beta(s,\tau)$}\label{fig:fsm:task:beta}}[0.45\textwidth]{
\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=7cm,thick,scale=0.6,every node/.style={scale=0.6},level distance=20mm]
\node[state,initial]
  (a)   {};
\node[state]
  (b) [right of=a]  {};
\path[]
(a)
  edge 
  node {$\bfjtt{duration}(\tau,\tau)$}
  (b)
(b)
  edge [bend right, above] 
  node [align=center] 
       {$\bfjtt{if}\big((1-\varepsilon_\beta(s,\tau)) > \beta(s,\tau)\big) $ 
       \\ \{ %\\
        $P \; ! \; \jtt{deallocate}(s,\tau)$ ; %\\
        $P \; ! \; \jtt{verify}_\beta(s,t_G)$ \}
       }
  (a)
;
\end{tikzpicture}
}
% \vspace{-10pt}
% \caption{{\scriptsize Task Automata for $\alpha(s,\tau,t_c)$ and $\beta(s,\tau)$}}
% \vspace{-10pt}
\end{figure}

We use a separate task automaton for each service characteristic to verify the SLA of the service after $t_G$ time.
Respectively, $M^{\alpha}_{\jtt{V}}$ and $M^{\beta}_{\jtt{V}}$ execute tasks $\jtt{verify}_\alpha$ and $\jtt{verify}_\beta$ (Figures~\ref{fig:fsm:task:verify:alpha} and \ref{fig:fsm:task:verify:beta}).
$M^{\alpha}_{\jtt{V}}$ uses \bfjtt{await} to ensure the condition of the SLA.
In addition, the task is controlled by the scheduler using a deadline that is specified as $t_G$ in the generated task $\jtt{verify}_\alpha(s,t_G)$ in $M_{\alpha_s}$. 
If $t_G$ passes before the guard statement in \bfjtt{await} statement holds, it leads to a \emph{missed deadline}.
\begin{figure}[h]
% \vspace{-20pt}
\captionsetup[subfigure]{font=scriptsize}
\centering
\subcaptionbox{\scriptsize{$M^{\alpha}_{\jtt{V}}$ to execute $\jtt{verify}_\alpha$}\label{fig:fsm:task:verify:alpha}}[0.45\textwidth]{
\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=6.5cm,thick,scale=0.6,every node/.style={scale=0.6},level distance=20mm]
\node[state,initial]
  (a)   {};
\node[state,accepting]
  (b) [right of=a]  {};
\path[]
(a)
  edge
  node [align=center] 
    {$\bfjtt{await} \; \alpha(s,\tau,t_c) \geq 1-\varepsilon_\alpha(s,\tau,t_c)$}
  (b)
;
\end{tikzpicture}
}%
\subcaptionbox{\scriptsize{$M^{\beta}_{\jtt{V}}$ to execute $\jtt{verify}_\beta$}\label{fig:fsm:task:verify:beta}}[0.45\textwidth]{
\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=6cm,thick,scale=0.6,every node/.style={scale=0.6},level distance=20mm]
\node[state,initial]
  (a)   {};
\node[state,accepting]
  (b) [right of=a]  {};
\path[]
(a)
  edge
  node [align=center] 
    {$\bfjtt{await} \; \beta(s,\tau) \geq 1-\varepsilon_\beta(s,\tau)$}
  (b)
;
\end{tikzpicture}%
}
% \vspace{-10pt}
% \caption{{\scriptsize Task automata to execute $\jtt{verify}_\alpha$ and $\jtt{verify}_\beta$}}
% \vspace{-10pt}
\end{figure}

@@

\begin{figure}[h]
% \vspace{-20pt}
\centering
\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=4cm,thick,scale=0.7,every node/.style={scale=0.7}]
\node[state,initial]    
  (a)   {};
\node[state]
  (b) [right of=a]   {};
\node[state,accepting]
  (c) [right of=b]  {};
\path[]
(a) 
    edge    
    node {$\bfjtt{duration}(t_i,\tau)$}          
    (b)
(b) 
    edge    
    node {$\sigma(s) \gets \sigma(s) + 1$} 
    (c)
;
\end{tikzpicture}
% \vspace{-15pt}
\caption{$M_{\jtt{A}_s}$: Timed Automaton to execute task type \jtt{allocate} in $M_P$}
% \vspace{-20pt}
\label{fig:fsm:alloc_s}
\end{figure}

Then, we define $M_{\jtt{A}}$ in $M_P$ as:
$M_{\jtt{A}} = \; \parallel_s M_{\jtt{A}_s}$; i.e.
the composition of all timed automata to execute a task \jtt{allocate} for some service $s$.
% 
Similarly, we design $M_{\jtt{D}_s}$ to execute task type \jtt{deallocate} in Figure~\ref{fig:fsm:dealloc_s}.
Therefore, we also have $M_{\jtt{D}}$ in $M_P$ as: $M_{\jtt{D}} = \; \parallel_s M_{\jtt{D}_s}$.
% 
\begin{figure}[h!]
% \vspace{-10pt}
\centering
\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=4cm,thick,scale=0.7,every node/.style={scale=0.7}]
\node[state,initial]    
  (a)   {};
\node[state]
  (b) [right of=a]   {};
\node[state,accepting]
  (c) [right of=b]  {};
\path[]
(a) 
    edge    
    node {$\bfjtt{duration}(t_i,\tau)$}          
    (b)
(b) 
    edge    
    node {$\sigma(s) \gets \sigma(s) - 1$} 
    (c)
;
\end{tikzpicture}
% \vspace{-15pt}
\caption{$M_{\jtt{D}_s}$: Timed Automaton to execute task type \jtt{deallocate} in $M_P$}
% \vspace{-20pt}
\label{fig:fsm:dealloc_s}
\end{figure}
%

@@

\begin{figure}[h]
% \vspace{-20pt}
\centering
\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=5cm,thick,scale=0.7,every node/.style={scale=0.7}]
\node[state,initial]
  (a) {};
\node[state]
  (b) [right of=a] {};
\node[state]
  (c) [right of=b] {};
\path[]
(a)
  edge
  node {$\bfjtt{duration}(0,\tau)$}
  (b)
(b)
  edge
  node {$\sigma(s)\gets\sigma(s)-c$}
  (c)
;
\end{tikzpicture}
% \vspace{-13pt}
\caption{An example behavior for $M_E$}
\label{fsm:env}
% \vspace{-20pt}
\end{figure}

### 2016-01-12 p03-ch02-2014-jmseq/jmseq-elsa.tex
Remove all `vspace`
Fix long captions in figures and tables

% \begin{wrapfigure}{r}{0.5\textwidth}
\begin{figure}[t]
\vspace{-30pt}
\begin{center}
\includegraphics[scale=0.7]{images/DM}
\end{center}
\vspace{-20pt}
\caption{Fredhopper's Controller life cycle for data processing requests from customers}
\label{fig:frh-dm}
\vspace{-5pt}
\end{figure}
% \end{wrapfigure}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.72]{images/frh-case-study-summary-rev2}
\caption{Result of experiment measurements without and with using JMSeq on Fredhopper Client API directed with live environment data from customers.}
\label{fig:frh:cs}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.55]{images/perf}
\caption{Comparison of different techniques applied to the same program. 
In this figure, ``original'' denotes the original program that is measured for execution time;
``instrumented'' denotes using a technique such as JavaMOP that uses instrumentation for verification;
 and ``original{\textbackslash}JMSeq'' denotes the measurement of the execution time for the program apart from times for JMSeq.}
\label{fig:jmseq-performance}
\end{center}
\end{figure}

>>>>

% \begin{wrapfigure}{r}{0.5\textwidth}
\begin{figure}[t]
% \vspace{-30pt}
\begin{center}
\includegraphics[scale=0.7]{images/DM}
\end{center}
% \vspace{-20pt}
\caption{Fredhopper's Controller life cycle for data processing requests from customers}
\label{fig:frh-dm}
% \vspace{-5pt}
\end{figure}
% \end{wrapfigure}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.72]{images/frh-case-study-summary-rev2}
\caption[Comparison of measurements using JMSeq at Fredhopper]{Result of experiment measurements without and with using JMSeq on Fredhopper Client API directed with live environment data from customers.}
\label{fig:frh:cs}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.55]{images/perf}
\caption[Comparison of different techniques with JMSeq]{Comparison of different techniques applied to the same program. 
In this figure, ``original'' denotes the original program that is measured for execution time;
``instrumented'' denotes using a technique such as JavaMOP that uses instrumentation for verification;
 and ``original{\textbackslash}JMSeq'' denotes the measurement of the execution time for the program apart from times for JMSeq.}
\label{fig:jmseq-performance}
\end{center}
\end{figure}
